Analysis of bulk void regions

### 2014-04-30 cosmic_voids.tex
Anlysis of the plot of FA vs Lambda_1. Tomography of the cosmic web.

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. For this, we shall use the distribution of dark matter halos as 
tracer of the underlying matter field in order to be more consistent with
available observational data. First, we analyse distributions of mass and 
peculiar velocity in order to assign typical values to each type of 
environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
both distributions for web schemes and using the FOF catalogue of the 
simulation. Thick lines correspond to the median of the distribution and 
filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
$Q_3$, it means, $50\%$ of all halos are within such regions for every 
\lth value and for each type of environment. We rather use median and 
quartiles as measure of dispersion because there are some very unusual and 
extreme values that makes the usual analysis based upon means and standard 
deviations less reliable.

A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
is the median mass for each region. In the case of the T-web, although 
dispersions of the distribution of mass for each environment are 
considerably overlapped each other, the median value is very 
well-differentiated among types of environment, indicating that it is 
possible to assign typical values of mass to each region, and being 
consistent with expectations, where low mass halos are typical in voids 
until high mass halos in knots. For the case of the V-web scheme, all
medians and dispersions are completely overlapped, specially for values 
grater than the optimal \lth value, indicating that it is not possible to
assign typical mass ranges to each environment as quantified by this 
scheme. For peculiar velocities, this situation is opposite, where V-web
scheme is much more adequate to assign typical distributions of velocity
to each environment. Although T-web also makes a differentiation in the 
distributions of velocity, this is very slight compared with the V-web 
case. These results can be explained by appealing the physical origin of 
each web scheme. As T-web is based upon the Hessian matrix of the 
potential field, it is expected all quantities related to the potential, 
like density field and distribution of halos mass, are well-differentiated 
among each region, while for the V-web scheme, based upon the shear 
velocity tensor, all dynamical quantities, as the peculiar velocity field 
and the distribution of halos velocity are alike expected to be 
well-differentiated among regions as quantified by this scheme.

Finally, we also calculate typical distributions of the density and 
peculiar velocity fields on the volume cells associated to each type of 
environment, obtaining completely analogous results. Furthermore, we use a 
BDM catalogue of the simulation as well, obtaining very similar conclusions.

@@

In order to overcome the percolation of voids in our classification scheme,
we introduce the fractional anisotropy as defined in \SRKED{[reference, 
Libeskind]}.

@@

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical property quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field around knots presents 
a very narrow distribution, whereas for the V-web the same distribution is
more spread. This can be explained appealing to the low dispersion of the 
density field with respect to the peculiar velocity in highly non-linear 
regions like knots. For more linear regions like voids, the behaviour of 
the FA field is quite similar between both schemes, what is consistent 
with the equivalence of the T-web and the V-web in the linear regime 
\SRKED{[reference, Hoffman]}.

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$, this implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_th$, all voids grow up progressively 
through contours of $\lambda_3$ field until certain critical value where 
voids are very large so the visual impression is no longer reliable.

@@

%.........................................................................
%FIGURE 1: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 2: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

@@

  \captionof{figure}{\small In left panels is shown the visual impression 
  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
  defined type of environments, where voids corresponds to white zones, 
  sheets to gray, filaments to dark gray and finally knots to black regions. 
  In the right panels is shown the fractional anisotropy field for the same 
  slide of the simulation and for each web schemes, where black regions 
  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
  degeneration of low values of FA for knots and central regions of voids, 
  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
  and highly planar sheets.}

@@

>>>>

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. For this, we shall use the distribution of dark matter halos as 
tracer of the underlying matter field in order to be more consistent with
available observational data. In the figure \ref{fig:halos_fractions} we 
calculate fractions of halos within each one of the defined environments 
based upon the FOF catalogue of the simulation and for an extensive \lth 
range. Then we look for some key feature that could indicated us a 
possible optimal value of the \lth value. One first step forward our quest 
is the behaviour of the V-web scheme compared with the T-web. As was 
previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
in the figure \ref{fig:halos_fractions}, V-web scheme is significantly more
sensible to variations of the $\lambda_{th}$ value, since all fractions of
halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
for the T-web scheme, fractions change smoothly throughout all \lth range 
covered. From this, it is then expected that the optimal \lth value for 
the V-web scheme is less than the T-web value.

The more notorious characteristic of the figure \ref{fig:halos_fractions} 
is the behaviour of the fraction of halos within sheet regions for both 
web schemes, increasing until a local maximum, and then decreasing. The 
increasing or decreasing rate of the fraction of halos for some region 
could be interpreted as a measure of the degree of non-linearity of such 
region for some specific \lth value. For example, filaments and knots, 
that are the most non-linear regions of the universe, have a negative rate
for all covered \lth range. In the case of voids, the situation is 
completely opposite, where fractions of halos increase in everywhere. If 
we think in terms of the underlying matter field of the cosmic web, \lth 
is just a cutting parameter between highly non-linear regions (filament 
and knots) and low non-linear (voids and sheets). Furthermore, if we take 
into account that dark matter halos are much more likely to form in highly 
non-linear regions, it is expected the obtained behaviour of the fractions 
of halos for voids, filaments and knots as we increase the \lth value. 
However, the behaviour of the fraction of halos in sheets is less clear,
increasing for low \lth values (such as voids) and decreasing for higher 
\lth values (such as filaments and knots). This indicates the transitional 
character of sheet regions in the cosmic web. Our proposal here is to 
select as optimal \lth the value where the fraction of sheets reaches a
local maximum. According to this, we find for the T-web scheme an optimal 
value $\lambda_{opt}^T = 0.36$ and for the V-web scheme $\lambda_{opt}^V = 
0.20$. In the figure \ref{fig:visual_impression} we show the visual 
impression of the cosmic web along with the density field for different 
\lth values including the optimal values. It can be noticed that the found 
optimal values reproduce well the visual impression.

As we have taken halos as tracers of the cosmic web, we analyse 
distributions of mass and peculiar velocity in order to assign typical 
values to each type of environment. In the figure 
\ref{fig:typical_mass_velocity} we calculate both distributions for both 
web schemes and using the FOF catalogue of the simulation. Thick lines 
correspond to the median of the distribution and filled regions limited by
dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
all halos are within such regions for every \lth value and for each type 
of environment. We rather use median and quartiles as measure of 
dispersion because there are some very unusual and extreme values that 
makes the usual analysis based upon means and standard deviations less 
reliable.

A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
is the median mass for each region. In the case of the T-web, although 
dispersions of the distribution of mass for each environment are 
considerably overlapped each other, the median value is very 
well-differentiated among types of environment, indicating that it is 
possible to assign typical values of mass to each region, and being 
consistent with expectations, where low mass halos are typical in voids 
until high mass halos in knots. For the case of the V-web scheme, all
medians and dispersions are completely overlapped, specially for values 
grater than the optimal \lth value, indicating that it is not possible to
assign typical mass ranges to each environment as quantified by this 
scheme. For peculiar velocities, this situation is opposite, where V-web
scheme is much more adequate to assign typical distributions of velocity
to each environment. Although T-web also makes a differentiation in the 
distributions of velocity, this is very slight compared with the V-web 
case. These results can be explained by appealing the physical origin of 
each web scheme. As T-web is based upon the Hessian matrix of the 
potential field, it is expected all quantities related to the potential, 
like density field and distribution of halos mass, are well-differentiated 
among each region, while the V-web scheme, based upon the shear velocity 
tensor, all dynamical quantities, as the peculiar velocity field and the 
distribution of the velocity of halos are also expected to be 
well-differentiated among regions as quantified by this scheme.

Finally, we also calculate typical distributions of the density and 
peculiar velocity fields in each type of environment, obtaining completely
analogous results. Furthermore, we also use a BDM catalogue of the 
simulation, obtaining very similar conclusions.

@@

In order to deal with percolation of voids in our classification scheme,
we introduce the fractional anisotropy as defined in \SRKED{[reference, 
Libeskind]}.

@@

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical properties quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field around knots presents 
a very narrow distribution, whereas for the V-web the same distribution is
more spread. This can be explained appealing to the low dispersion of the 
density field compared with the peculiar velocity in highly non-linear 
regions like knots. For more linear regions like voids, the behaviour of 
the FA field is quite similar between both schemes, what is consistent 
with the equivalence of the T-web and the V-web in the linear regime 
\SRKED{[reference, Hoffman]}.

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_{th}$, all voids grow up 
progressively through contours of the $\lambda_3$ field until certain 
critical value where they are so large that the visual impression is no 
longer reproduced. Our objective here is to find a reliable quantity that 
allows to trace the geometry of void regions as classified by each web 
scheme. In the figure \ref{fig:L1_correlations} we calculate the 
distributions of the fractional anisotropy index and the density field 
regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
cells of the simulation. Thick lines correspond to the median of the 
distributions, whereas coloured regions correspond to the $50\%$ of the
sample, delimited by quartiles $Q_1$ and $Q_3$.

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids and they are the more 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions, the FA index increases as well, maintaining a perfect correlation 
approximately until the optimal threshold value for each scheme. Because 
of the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$. 
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
threshold, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the optimal
threshold is a limit value up to which we can have void regions. For other
type of environment such as sheets, filaments and knots, the $\lambda_1$
eigenvalue does not control their spatial boundaries, so the correlation
with the FA index is no longer valid. The larger dispersion in the 
distribution indicates that contours of the FA field are no longer 
corresponding to contours of the $\lambda_1$ field. Nevertheless, for high
$\lambda_1$ values, i.e. $\lambda_1>1.0$, the median value of the FA index
decreases to lower values, indicating the presence of isotropic knots. All
of this allows us to conclude that the distribution of the FA with respect
to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
voids, but also an one-dimensional projection of the global structure of
the cosmic web, starting in highly isotropic central voids, passing 
through very anisotropic sheets and filaments, until isotropic knot 
regions.

@@

%.........................................................................
%FIGURE 1: Fraction of halos in each environment
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}  
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}

  \captionof{figure}{\small Fractions of halos embedded in each one of 
  the defined environments according to the \lth value. T-web scheme 
  (left panel) and V-web scheme (right panel). The optimal parameters 
  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}

  \label{fig:halos_fractions}
  \vspace{0.1 cm}

%.........................................................................
%FIGURE 2: Visual impression of the cosmic web
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}

  \captionof{figure}{\small Visual impression of the density field (left 
  panels), and of each classification scheme with the $\lambda_{th}$ values 
  obtained by our criteria (others panels). The color convention for each 
  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
  (black) - knot. For each web scheme, it has been used the previously 
  established optimal threshold as a reference value, so plots are done 
  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
  2\lambda_{opt}$.}

  \label{fig:visual_impression}
  \vspace{0.1 cm}

%.........................................................................
%FIGURE 3: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 4: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

@@

  \captionof{figure}{\small In left panels is shown the visual impression 
  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
  defined types of environment, where voids corresponds to white zones, 
  sheets to gray, filaments to dark gray and finally knots to black regions. 
  In the right panels is shown the fractional anisotropy field for the same 
  slide of the simulation and for each web schemes, where black regions 
  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
  degeneration of low values of FA for knots and central regions of voids, 
  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
  and highly planar sheets.}

@@

%.........................................................................
%FIGURE 5: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/FA_L1.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/delta_L1.pdf}

  \captionof{figure}{\small In this figure is shown the distribution of the
  fractional anisotropy (left panel) and density field (right panel) with 
  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
  lines. V-web, blue lines) as calculated over all the cells of the grid.
  Thick central lines correspond to the median of the distribution and 
  coloured regions to the $50\%$ of the cells, delimited by quartiles 
  $Q_1$ and $Q_3$.}

  \label{fig:L1_correlations}
  \vspace{0.1 cm}
